---
title: "NJN-Korrelatoren"
author: "Timo Beilschmidt"
date: "\\today"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(hadron)
library(Raff)
library(pracma)
library(binhf)
library(boot)
source('/qbigwork2/beilschmidt/code/R/get_sl.R')
source('/qbigwork2/beilschmidt/code/R/R_gamma.R')
#options(warn = -1)#, error=recover)
trace <- function(A) {
  n <- dim(A)[1] # get dimension of matrix
  tr <- 0 # initialize trace value
  
  # Loop over the diagonal elements of the supplied matrix and add the element to tr
  for (k in 1:n) {
    l <- A[k,k]
    tr <- tr + l
  }
  return(tr[[1]])
}

projector <- function(sgn, gamma0){
  p <- array(0, dim = c(4,4))
  for (a in c(1:4)) {
    for (b in c(1:4)) {
      if (a == b) {
        p[a,b] <- 0.5
      } else {
        p[a,b] <- 0.5 * sgn * gamma0[a,b]
      }
    }
  }
  return(p)

}

read_dia <- function(key, nrDiagram=4, file_str, src_str_alt, gi= "Gi_Cg5", gf = "Gf_Cg5"){

    diagrams <- list()
    corrKey <- key
    for (t in c(1:nrDiagram)) {
          t_name <-  paste("t",toString(t), sep = "")
          key_str <- paste("/",corrKey,"/", src_str_alt,"/",gf,"/Gc_id/",gi,"/QX0_QY0_QZ0/",t_name,"/px00py00pz00", sep = "")
          d <- aff_read_key(file_str, key_str, 1024)
          #diagrams[t_name] <- raw_cf_data(cf = raw_cf_meta(Time=T, dim=c(4,4)),
          #                                  data = aperm(array(d, dim = c(4, 4, 64)), c(3,1,2)))
          diagrams[[t_name]] <- array(d, dim = c(4, 4, 64))
     }
    return(Reduce('+', diagrams))    
}

```

## NN-Correlator

```{r analyze, echo=FALSE, results='asis'}
##############################################################
#Setting up variables to look at
##############################################################

proj_sign = 1
gi= "Gi_Cg5"
gf = "Gf_Cg5"


###############################################################
#main function for analyzing correlator function 
###############################################################

analyze <- function(corrKey = "N-N",pathToData="/hiskp4/petschlies/nucleon-ff/cA211a.30.32/J125-k0p2/",T=64, n_src = 16,n_conf = 1224, projector_sign = 1, gi= "Gi_Cg5", gf = "Gf_Cg5"){
  # Read in data
  # n_conf <- 1224
  # n_src <- 16
  # T <- 64
  #conf <- 792
  cor <- array(0, dim = c(T, n_src, (n_conf/24+1)))
  cor_final <- array(0, dim = T)
  cor_std <- array(0, dim = T)
  #nn_cor <- array(0, dim = T/2)
  #nn_std <- array(0, dim = T/2)
  cor_mean_src <- array(0, dim = c(T, (n_conf/24+1)))
  #cor_conf <- array(0, dim = c(T/2, (n_conf/24+1)))
  #load gamma matrices
  g <- set_gamma_basis_all(g=gamma_basis$tmlqcd)
  #load Cxgamma, but without i factor and multiply with i
  Cg <- set_Cgamma_basis_matching( g=gamma_basis$tmlqcd  )
  
  # generate projektor matrix
  p <- projector(projector_sign, g$`0`)
  # Source coord list
  source_list <- get_source_coords_table(f = paste("/hiskp4/beilschmidt/nucleon-ff/job_submit","source_coords.cA211a.30.32.nsrc16.tab", sep = "/"))
  
 print(sprintf("%s, T=%i, n_src=%i, n_conf=%i, projector_sign = %i, Gi = %s, Gf = %s", corrKey, T, n_src, (n_conf/24+1), projector_sign, gi, gf))
  for (conf in seq(0, n_conf, 24)){
    for (src in c(1:n_src)) {
      
      src_str <- get_source_coords_tag(c = conf, i=src, sl = source_list)
     
      # Open File
      file_str <- paste(pathToData,"njn_fht.",formatC(conf, width = 4, flag = "0"),".", src_str,".aff", sep="")
      src_str_alt <- toupper(src_str)
      
      for (i in c(2:4)) {
        tmp_str <- unlist(strsplit(src_str_alt, ""))
        ind <- grep("[A-Z]", tmp_str)[i]
        src_str_alt <- paste0(c(tmp_str[1:(ind-1)], "_", tmp_str[ind:(nchar(src_str_alt))]), collapse="")
      }
      
      if(strcmp(corrKey, "N-N")){      
        key_str <- paste("/",corrKey,"/", src_str_alt,"/",gi,"/",gf,"/n1/px00py00pz00", sep = "")
        d <- aff_read_key(file_str, key_str, 1024)
        # create SpinxSpinxTime matrix n1
        n1 <- array(d, dim = c(4, 4, 64))
        #cf_n1 <- raw_cf_data(cf = raw_cf_meta(Time=T, dim=c(4,4)),
        #                                    data = aperm(n1, c(3,1,2)))
        #cf_n1 <- cvc_to_raw_cf_test(d, dims=c(4,4))
        key_str <- paste("/",corrKey,"/", src_str_alt,"/",gi,"/",gf,"/n2/px00py00pz00", sep = "")
        d <- aff_read_key(file_str, key_str, 1024)

        # create SpinxSpinxTime matrix n2
        n2 <- array(d, dim = c(4, 4, 64))
        #cf_n2 <- raw_cf_data(cf = raw_cf_meta(Time=T, dim=c(4,4)),
        #                                    data = aperm(n2, c(3,1,2)))
        #cf_n2 <- cvc_to_raw_cf_test(d, dims=c(4,4))

        nn <- n1 + n2
        
      } else if (strcmp(corrKey, "N-ubGu-N")) {

            nn <- read_dia(corrKey, nrDiagram =4 , file_str, src_str_alt)
      } else if (strcmp(corrKey, "N-dbGd-N")) {

            nn <- read_dia(corrKey, nrDiagram =2 , file_str, src_str_alt)

      } else if (strcmp(corrKey, "N-J-N")) {
            
            nn <- read_dia("N-ubGu-N", nrDiagram =4 , file_str, src_str_alt)
            nn <- nn + read_dia("N-dbGd-N", nrDiagram =2 , file_str, src_str_alt)

      }
      #is.raw_cf(nn)
      #get_plotdata_raw_cf(nn, "both", TRUE, TRUE) 
      # get soruce time
      t_src <- matrix(unlist(strsplit(src_str_alt, "_")))[1]
      t_src <- strtoi(substring(t_src, 2, nchar(t_src)))
      
      # add phasefactor
      for (t in c(1:T)) {
        del_t <- (T + t-1 - t_src) %% T
        phasefactor <- exp(1i * 3 * pi * del_t / T)
        nn[,,t] <- nn[,,t]*phasefactor
        # multiply projection matrix and take trace
        cor[t,src,(conf/24+1)] <- trace(p %*% nn[,,t])
      } # end time loop
      
      # shift source location to 0
      cor[,src,(conf/24+1)] <- shift(cor[,src,(conf/24+1)], t_src, dir = "left")
    } # end source loop
    
   
    # mean of source contribution
    for (t in c(1:T)) {
      cor_mean_src[t,(conf/24+1)] <- mean(cor[t,,(conf/24+1)])
    }
  
  } # end loop conf
  
      
  for (t in c(1:T)) {
    cor_final[t] <- mean(Re(cor_mean_src[t,]))
    cor_std[t] <- sqrt(var(Re(cor_mean_src[t,]))/(n_conf))
  }
  # Symmetrize
  #for (t in c(1:T/2)) {
   # nn_cor[t] <- (cor_final[t] + cor_final[T-t+1])/2
    #nn_std[t] <- sqrt(cor_std[t]*cor_std[t] + cor_std[T-t+1]*cor_std[T-t+1])/2
    #cor_conf[t,] <- (cor_mean_src[t,] + cor_mean_src[T-t+1,])/2

  #}
  print("Not symmetrized:")
  print(cor_final)
  #knitr::kable(cor_final, caption="Not symmetrized correlator")
  #return(list("cor"=nn_cor, "std"=nn_std, "T"=T, "cor_conf"=cor_conf))
  return(list("cor"=cor_final, "std"=cor_std, "cor_conf"=cor_mean_src , "T"=T))
}
```

```{r 2pt_calc, echo=FALSE}
c2<- analyze(corrKey = "N-N", projector_sign = proj_sign, gi= gi, gf = gf)
```



```{r 2pt_plot, echo=FALSE}
plotCor <- function(c, title="N-N Correlator", legend_title="N-N"){
	df <- data.frame(t=c(1:(c$T)), C= c$cor, std= c$std)
	plot(x=df$t, y=(df$C), main = title ,ylab = "Corr",xlab = "t", xlim=c(1,32),col="blue",  pch=1, cex.main=1.5, frame.plot=FALSE, log = "y")
	arrows((df$t), (df$C-df$std),(df$t), (df$C+df$std), length=0.05, angle=90, code=3)
	legend("topright",c(legend_title),cex=.8,col=c("blue"),pch=c(1))
        #print(df$C)
}
plotCor(c2)
```
\pagebreak

### Effective Mass

We calculate the effective mass following  <https://arxiv.org/abs/1612.06963>.

$m^{eff}(t,\tau)=\frac{1}{\tau}ln\left(\frac{C(t)}{C(t+\tau)}\right)\rightarrow_{t\rightarrow \infty} \frac{1}{\tau}ln(e^{E_0\tau})=E_0$

```{r mass_meth, echo=FALSE}

colVec <- c("black", "red", "limegreen", "blue", "yellow", "cyan", "magenta", "maroon")

m_eff <- function( mat, index, tau=1, tsize ){
  i <- sample(c(1:52), size=52, replace=TRUE)
  d <- apply ( mat[,i], c(1), mean )
  idt1 <- ( 0 : ( tsize - tau ) ) + 1
  idt2 <- idt1 + tau

  return ( log ( d[idt1] / d[idt2] ) / tau )
}

m_boot <- function ( corr, R, tau, tsize ) {
  r <- boot(data=corr, R=R, statistic = m_eff, tsize=tsize )
  nt <- dim(r$t)[2]

  df <- data.frame (t= 0:(nt-1), rep(tau, times=nt),m= r$t0[1:nt],std= apply (r$t, c(2), sd ), r$t0[1:nt]-apply(r$t, c(2), mean )  )
  #write.table( df, file="m_boot.tmp", col.names=F, row.names=F )
  return( invisible ( df ) )
}
 #m_std <- apply(c$cor_conf,2,sd, na.rm = TRUE)

corr_mean <- function(mat, index) {
#  cat ( "# [corr_mean] index = ", index, "\n" )
#  cat ( "# [corr_mean] str ( mat ) = ", str( mat), "\n" )

  return( apply ( mat[,index], c(1), mean ) )
}


```

```{r mass_plot, echo=FALSE}
plotM <- function(c){
	df <- m_boot(corr = c$cor_conf, R = 5000, tau = 1, tsize = c$T)
	plot(x=df$t[1:(c$T-1)]+1 , y=(df$m[1:(c$T-1)]), main = "N-N Correlator effective mass",ylab = "m_eff",xlab = "t", xlim=c(1,30),ylim = c(.15, 1.5) ,col=colVec[1],  pch=1,cex=0.8, cex.main=1,lwd = 0.3, frame.plot=FALSE)
	arrows((df$t[1:(c$T-1)]+1), Re(df$m[1:(c$T-1)]-df$std[1:(c$T-1)]),(df$t[1:(c$T-1)]+1), Re(df$m[1:(c$T-1)]+df$std[1:(c$T-1)]), length=0.05,lwd=.3, angle=90, code=3)
	for (ttau in c(2:8)) {
	   
	  df <- m_boot(corr = c$cor_conf, R = 5000, tau = ttau, tsize = c$T)
	  points(x=df$t[1:(c$T-1)]+1, y=(df$m[1:(c$T-1)]), pch=ttau,cex=0.8, col=colVec[ttau], lwd = 0.3)
	  arrows((df$t[1:(c$T-1)]+1), Re(df$m[1:(c$T-1)]-df$std[1:(c$T-1)]),(df$t[1:(c$T-1)]+1), Re(df$m[1:(c$T-1)]+df$std[1:(c$T-1)]), length=0.05, angle=90, code=3, lwd = .3)
	}
	legend("topleft",c("tau = 1","tau = 2","tau = 3","tau = 4","tau = 5","tau = 6","tau = 7","tau = 8"),cex=.8,col=colVec,pch=c(1:8))
}
plotM(c2)

#analyze(corrKey = "N-N")
```

\pagebreak

## NJN-Correlator


First the 3pt-function correlator:


```{r 3pt, echo = FALSE}
c3 <- analyze(corrKey = "N-J-N", projector_sign = proj_sign, gi= gi, gf = gf)
plotCor(c3, title="3pt-function Correlator", legend_title="N-J-N")
```
\pagebreak

###Ratio-Plot


$\left. \frac{\partial m_\lambda^{eff}(t,\tau)}{\partial \lambda} \right|_{\lambda=0}= \frac{1}{\tau}\left( \frac{\partial_\lambda C_\lambda(t)}{C(t)}- \frac{\partial_\lambda C_\lambda(t+\tau)}{C(t+\tau)}   \right)_{\lambda=0}$



```{r ratio_plot, echo=FALSE}

ratio <- function( c2pt, index, c3pt, tau=1 ){
  i <- sample(c(1:52), size=52, replace=TRUE)
  c2 <- apply(c2pt$cor_conf[,i], c(1), mean)
  c3 <- apply ( c3pt$cor_conf[,i], c(1), mean )
  idt1 <- ( 0 : ( c2pt$T - tau ) ) + 1
  idt2 <- idt1 + tau

  return ( ( Re(c3[idt1]) / Re(c2[idt1]) - Re(c3[idt2])/Re(c2[idt2]) ) / tau )
}

boot_Ratio <- function(c2, c3, R=5000, tau =1){
    
    r <- boot(data = c2, R=R, statistic = ratio, c3pt=c3, tau=tau)
    nt <- dim(r$t)[2]
    df <- data.frame (t= 0:(nt-1), rep(tau, times=nt),m= r$t0[1:nt],std= apply (r$t, c(2), sd ), r$t0[1:nt]-apply(r$t, c(2), mean )  )
    #write.table( df, file="m_boot.tmp", col.names=F, row.names=F )
    return( invisible ( df ) )
}
plot_Ratio <- function(c2, c3){
    df <- boot_Ratio(c2, c3, R=5000)
    plot(x=df$t[1:(c2$T-1)]+1 , y=Re(df$m[1:(c2$T-1)]), main = "N-J-N linear response of effective mass to external bilinear current",ylab = "g_00",xlab = "t", xlim=c(0,30),ylim = c(-25, 50) ,col=colVec[1],  pch=1,cex=0.8, cex.main=1,lwd = 0.3, frame.plot=FALSE)
    arrows((df$t[1:(c2$T-1)]+1), Re(df$m[1:(c2$T-1)]-df$std[1:(c2$T-1)]),(df$t[1:(c2$T-1)]+1), Re(df$m[1:(c2$T-1)]+df$std[1:(c2$T-1)]), length=0.05,lwd=.3, angle=90, code=3)
    print(sprintf("tau = %i", 1))
   print(Re(df$m))
    for (ttau in c(2:8)) {
                   
        df <- boot_Ratio(c2,c3, R = 5000, tau = ttau)
        points(x=df$t[1:(c2$T-1)]+1, y=Re(df$m[1:(c2$T-1)]), pch=ttau,cex=0.8, col=colVec[ttau], lwd = 0.3)
        arrows((df$t[1:(c2$T-1)]+1), Re(df$m[1:(c2$T-1)]-df$std[1:(c2$T-1)]),(df$t[1:(c2$T-1)]+1), Re(df$m[1:(c2$T-1)]+df$std[1:(c2$T-1)]), length=0.05, angle=90, code=3, lwd = .3)
    print(sprintf("tau = %i", ttau))
   print(Re(df$m))
    }
	legend("topleft",c("tau = 1","tau = 2","tau = 3","tau = 4","tau = 5","tau = 6","tau = 7","tau = 8"),cex=.8,col=colVec,pch=c(1:8))
    return(invisible(df))
}

plotData <- plot_Ratio(c2, c3)

#Re(plotData$m)



```

